---
fontsize: 11pt
geometry: margin=1in
output: pdf_document
---

``` {r echo = FALSE, fig.height = 4, fig.width = 4, fig.align='right'}
library(png)
library(grid)
img <- readPNG('student-number.png')
grid.raster(img)
```

&nbsp;

``` {r echo = FALSE, fig.height = 2, fig.width = 2}
library(jpeg)
library(grid)
img <- readJPEG('Oxley-crest.jpg')
grid.raster(img)
```

&nbsp;

&nbsp;

Term 1

February 

2016


### Stage 6 - Year 12

# Maths General Task 2

### Task 2 - 25%

-------------------------------

**General Instructions**

* Time allowed: 45 minutes
* Write using a blue or black pen
* Board approved calculators can be used
* In all questions show relevant mathematical reasoning and/or calculations

**Total Marks - 30**

\newpage

Section I
=====================================

| **10 marks** 
| **Attempt questions 1 - 10** 
| **Allow about 10 minutes for this section**

--------------------------------------

**1** \text{     } Simplify $(3b^4)^2$

(A) $9b^{16}$

(B) $6b^8$

(C) $9b^6$

(D) $9b^8$

&nbsp;

**2** \text{     } Solve the equation: $$\frac{5w-3}{6}=8$$

(A) $w=13.6$

(B) $w=10.8$

(C) $w=10.2$

(D) $w=9.8$

&nbsp;

**3** \text{     } What best describes the shape of the following data set:

``` {r echo = FALSE, fig.width = 5, fig.height = 2.5, fig.align = 'center'}
data <- data.frame(Score = c(3,4,4,5,3,5,8,5,7,9,7,7,6,13,17,22,15,25))
boxplot(data, horizontal = TRUE)
```

(A) Bi-modal

(B) Symmetrical

(C) Positively Skewed

(D) Negatively Skewed

\newpage

**4** \text{     } Solve the equation: $$\frac{5w-3}{6}=8$$

(A) $w=13.6$

(B) $w=10.8$

(C) $w=10.2$

(D) $w=9.8$

&nbsp;


\newpage

Section II
=====================================

| **20 marks**
| **Attempt Questions 11 - 12**
| **Allow about 35 minutes for this section**

Answer each the questions in the spaces provided

Your responses should include relevant mathematical reasoning and/or calculations.

Extra writing space has been provided on pages 11 and 12. If you use this space, clearly indicate which question you are answering. 

--------------------------------------------------------

**Question 11** (10 marks)

(a) Expand $2y(5y^{2}-y^{3})$ **\hfill 1**

\huge.........................................................

.........................................................

.........................................................

\normalsize

&nbsp;

(b) Solve these equations to find the values of $x$ and $y$ **\hfill 3**

$$\begin{cases}2x+y=5\\2x-y=9\end{cases}$$

\huge.........................................................

.........................................................

.........................................................

.........................................................

.........................................................

.........................................................

.........................................................

\normalsize
\newpage

Solutions
=========================================

### Section I - Multiple Choice

| Question | Answer |
| -------: | ------ |
| 1        |  D     |
| 2        |  C     |
| 3        |  C     |
| 4        |  A--     |
| 5        |  A--     |
| 6        |  A--     |
| 7        |  A--     |
| 8        |  A--     |
| 9        |  A--     |
| 10       |  A--     |

### Section II - Written response

Some answers

